FraCaS: Temporal Analysis

### 2020-06-04 paper2020/paper.tex
revise and notes in background sec.

\paragraph{GF}
We work on a syntactic representation of the FraCaS test suite in GF
abstract syntax~\citep{Ljunglof:2012}. Thus, we skip the
parsing phase and avoid any syntactic ambiguity.

For the purpose of this paper, the important point is that GF the
syntax aims at a balance of sufficient abstraction to provide a
semantically-relevant structure, but at the same time it embeds
sufficiently many syntactic features to be able to reconstruct
unambiguously natural-language text. Example \label{ex:onelingex}
shows an example abstract syntax tree and its realisation in English.

\paragraph{Coq}
 Coq is an interactive theorem prover (proof assistant). It is based on the
calculus of coinductive constructions (CiC), i.e.  a lambda calculus
with dependent types and coinduction (we do not use any coinduction in this paper).  Coq is a very powerful reasoning engine
that makes it fit for implementing natural language semantics in it but also, on a more practical side, for the the task of NLI, when the latter is formalized
as a theorem proving task. Coq supports, as already mentioned,
 dependent typing, but also subtyping, which are instrumental in
expressing NL semantics.

@@

\paragraph{Temporal Semantics}
Stergios

>>>>

\paragraph{GF}
The grammatical framework (GF, \citet{Ranta:GF}) is a powerful parser
generator for natural languages, based on type-theoretical abstract grammars.
This work relies a syntactic representation of the FraCaS test suite in GF
abstract syntax~\citep{Ljunglof:2012}. Thus, we skip the parsing phase
and avoid any syntactic ambiguity.

For the purpose of this paper, the important point is that GF the
syntax aims at a balance of sufficient abstraction to provide a
semantically-relevant structure, but at the same time it embeds
sufficiently many syntactic features to be able to reconstruct
unambiguously natural-language text. \cref{ex:onelingex}
shows an example abstract syntax tree and its realisation in English.

\paragraph{Coq}
Coq is an interactive theorem prover (proof assistant). It is based on
the calculus of coinductive constructions~\citep{werner_une_1994} We
do not use any coinduction (or even induction) in this paper, relying
on the pure lambda-calculus inner core of Coq.  Coq is a very
powerful reasoning engine that makes it fit for implementing natural
language semantics in it but also, on a more practical side, for the
the task of NLI, when the latter is formalized as a theorem proving
task. Coq supports, as already mentioned, dependent typing, but also
subtyping, which are instrumental in expressing NL semantics.

@@

\paragraph{Temporal Semantics}
\todo{More general notion of temporal semantics? Should this be moved somewhere else?}
